Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-01-31 tacl.tex
Correct typos & typography
Fix to Fig 1; low-level edits throughout; bib fixes

% TJB macros
\newcommand{\dotts}{...}
\newcommand{\gap}{$*$\xspace}
\newcommand{\ex}[1]{\textit{#1}\xspace}
\newcommand{\termdef}[1]{\textbf{#1}\xspace}
\newcommand{\termemph}[1]{\textit{#1}\xspace}

@@

In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of \newcite{Wray02} and \newcite{Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a formulaic sequence shows signs of being part of a mental lexicon. Though by this definition individuals or small groups may have their own FS, here we are only interested in FSs that are shared by a recognizable language community.

In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} or ``MWE'' \cite{Sag02,Baldwin10}, but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a near superset which includes many MWEs but also (apparently) compositional linguistic formulas. This distinction is not a new one; it exists, for example, in the original paper of \newcite{Sag02} in the distinction between lexicalized and institutionalized phrases, and also to some extent in the MWE annotation of \newcite{Schneider14a}, who distinguish between weak (collocational)\footnote{Here we avoid the term \emph{collocation} entirely due to confusion with respect to its interpretation. Though in some contexts it has been used in a way that is similar to our definition of FS, it can be applied to any words that show a statistical tendency to appear in the vicinity of one another for any reason: for instance, the pair of words \ex{doctor/nurse} might be considered a collocation \cite{Ramisch14}.}  and strong (non-compositional) MWEs. It is our contention, however, that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we inclined to disregard the larger formulaticity of language simply because it is not the dominant focus of MWE research. Many MWE researchers might defensibly balk at including in their MWE lexicons and corpus annotations (English) formulaic sequences such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \gap weight in gold}, fall under the FS umbrella. Another reason to introduce a different terminology is that there are classes of what is typically considered MWE that do not fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{plastic house}). Also, we exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs.\ Barbara W.\ Smith} or \ex{Smith Garden Supplies Ltd}). \figref{fig:terminology} shows the conception of the relationship between FS, MWE, and (multiword) named entities that we assume for this paper.

@@

Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has been typically lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}; when these methods are used to build a lexicon, particular syntactic patterns and thresholds for the metrics are typically chosen. Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words. Other measures specifically designed to address sequences of larger than two words include the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones, and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word. Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase. Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word \cite{Riedl15}.

@@

The motivation for building lexicons of formulaic sequences naturally overlaps with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}. One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses. Within corpus linguistics, multiword sequences have been studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold. Like FS, Lexical bundles generally involve larger phrasal chunks that would be missed by traditional MWE extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indicative of particular genres (\eg university lectures). Lexical bundles have been applied, in particular, to learner language: for example,  \newcite{Chen10} show that non-native student writers use a severely restricted range of lexical bundle types, and tend to overuse those types, while \newcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners. \newcite{Sakaguchi16} demonstrate that improving fluency (closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; \newcite{Brooke15b} explicitly argue for FS lexicons as a way to identify, track, and improve learner proficiency.

@@

Our approach to FS identification involves optimization of the total explanatory power of a lattice, where each node corresponds to an $n$-gram type. The explanatory power of the whole lattice is defined simply as a product of the \termdef{explainedness} of the individual nodes. Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS). The basis of \termdef{explainedness} calculation is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.  Given these relationships, we iterate over the nodes and greedily optimizing the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.

@@

The first step in the process is to derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text. Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage. An initial requirement of any such method is an $n$-gram frequency threshold, which for us (following \newcite{Brooke15b}) is 1 instance per 10 million words.\footnote{Based on manual analysis using the MWE corpus of \newcite{Schneider14a}, this achieves very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names.} 
Note that our set of $n$-grams also includes gapped or non-contiguous $n$-grams, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}. Having said this, there are generally strong syntactic and length \cite{Wasow:2002} restrictions on what can constitute a gap, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall. We also exclude punctuation and lemmatize the corpus, and enforce an $n$-gram count threshold. As long as the count threshold  is significantly above 1, efficient extraction of all $n$-grams can be done iteratively: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold.

Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate the \termdef{Lexical Predictability Ratio} (``LPR'') for each word in the $n$-gram are collected. LPR measures how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words). Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$, is given by:
\begin{displaymath}
\LPR(w_i,w_{1,n}) = \max_{1 \leq j < k \leq n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
\end{displaymath}
where $w_{j,k}$ denotes the word sequence $w_j,..., w_{i-1}, w_{i+1}, ..., w_{k}$ excluding $w_{i}$ (similarly for $t_{j,k}$). Note that the lower bound of LPR is 1, since the ratio for a word with no context is trivially 1. We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics. %Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result.

In the segmentation approach of \newcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence (``\minLPR''):
\begin{displaymath}
\minLPR(w_{1,n}) = \min_{1 \leq i \leq n }{\LPR(w_i,w_{1,n})}
\end{displaymath}
Here, minLPR for a particular $n$-gram does not reflect the \emph{overall} degree to which it holds together, but rather focuses on the word which is its weakest link. For example, in the case of \ex{be keep \gap under}, a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.

%\footnote{Recall that our method involves lemmatization, in keeping with which all examples will be presented pre-lemmatized.}

@@

Let $E_{1}$ be the explainedness of a node when it is on (corresponding to an $n$-gram which has been identified as an FS), and $E_{0}$ be the explainedness of a node when it is off. We calculate $E_{0}$ based on the inverse of minLPR: 
\begin{displaymath}
E_0(t) = \minLPR(t)^{-d_0(t)}
\end{displaymath}
and $E_{1}$ based on the inverse of a cost parameter $C$:
\begin{displaymath}
E_1(t) = C^{-d_1(t)}
\end{displaymath}
where $d_0$ and $d_1$ are a non-negative functions which capture the lattice context (when there is no context, both default to 1), as detailed in the next section. When the minLPR metric is 1 (corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$. $E_1$ is equivalent to the initial threshold for building a vocabulary using the minLPR association measure for nodes not influenced by one of the other factors discussed below: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS. There is no upper bound on $C$, but empirically, we have found a value in the range $[3,6]$ gives reasonable results for the languages presented in this paper.% we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.

@@

\subsubsection{Covering}
The most important node interaction is \termdef{covering}, which corresponds to discounting or entirely excluding a node due to a node higher in the lattice. Our model includes two types of covering: hard and soft. \termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other. In \figref{fig:example}, \eg if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and we should consider these two $n$-grams as one. We do this by permanently disabling any hard covered node, and setting the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover. This is done as a preprocessing step, and greatly improves the tractability of the iterative optimization of the lattice. Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant majority of the counts of a lower node corresponding to the higher node) works well.  We also use the concept of hard covering to address the issue of pronouns: due to pragmatic biases, pronouns often have higher than desirable LPR values \cite{Brooke15b}. In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to limit FS with pronouns without excluding them entirely: they are included only in cases where they are definitively formulaic.

@@

A simple but effective solution which avoids introducing extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase $E_{0}$ of the higher node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(u_i)}\Big)}
\end{displaymath}
where $u_i$ is the $i$th clearing node of $t$. We refer to this mechanism as clearing because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5.

@@

The third mechanism of node interaction involves $n$-grams which overlap in the corpus. In general, independent formulaic sequences do not predictably overlap. For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR. To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes---a penalty rather than an incentive which expresses the model's confusion at having overlapping FS. Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to turned-on nodes which overlap with our target node $t$. We define $d_1(t)$, the exponential term for $E_1(t)$, as:
\begin{displaymath}
	d_{1}(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{\mathit{oc}(o_i)}}
\end{displaymath}

@@

@@

 \begin{center}
	 \label{tab:stats}
	 %\begin{tabular}{lc@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c@{\,\,\,}c}
	 \begin{tabular}{lrrrrr}

       \toprule
       & \multicolumn{2}{c}{Contiguous} & \multicolumn{2}{c}{Gapped} & \\
       \cmidrule(lr){2-3}\cmidrule(lr){4-5}
			& FS & non-FS & FS & non-FS & $\kappa$ \\
			 \midrule
			ICWSM & 169 & 702 & 29 & 916& 0.84 \\
			BNC & 49 & 403 & 8 & 475 & 0.84 \\
			Croatian & 64 & 382 & 11 & 456 & 0.87 \\
			Japanese & 124 & 286 & 36 & 341 & 0.81\\
       \bottomrule
 \end{tabular}
  %\caption{ Statistics for test sets (``Cont'' = contiguous; ``Gap'' = gapped)}
  \caption{ Statistics for test sets }

@@

\newcite{Brooke15b} introduced a method for evaluating formulaic sequence extraction without a reference lexicon or direct annotation of the output of a model. Instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model. We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: after training and based on written guidelines derived from the definitions of \newcite{Wray08}, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.

@@

 \end{tabular}
  \caption{ Results of formulaic sequence identification in various test sets; PMIrank = lexicon created by ranking pointwise mutual information, minLPRrank = lexicon created by ranking by minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score. Bold is best in column.}
	 \label{tab:main}

@@

       \toprule
			& P & R & F\\
			 \midrule
			PMIrank & 0.20 & 0.29 & 0.23 \\
			minLPRrank & 0.34 & 0.45 & 0.39 \\
			LPR-seg & 0.42 & 0.45 & 0.43 \\
			LocalMaxs & \bf{0.56} & 0.39 & 0.46 \\
			DP-seg & 0.35 & \bf{0.71} & 0.47 \\
			Lattice & 0.47 & 0.63 & \bf{0.54} \\
       \bottomrule
 \end{tabular}
  \caption{ Results of formulaic sequence identification in contiguous BNC test set; LocalMaxs = method of Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
	\label{tab:BNC}

>>>>

% TJB macros
\newcommand{\dotts}{...}
\newcommand{\gap}{$*$\xspace}
\newcommand{\z}{\phantom{0}}
\newcommand{\ex}[1]{\textit{#1}\xspace}
\newcommand{\termdef}[1]{\textbf{#1}\xspace}
\newcommand{\termemph}[1]{\textit{#1}\xspace}

@@

In this paper we will refer to the targets of our lexicon creation efforts as \termdef{formulaic sequences}, following the terminology of Wray \shortcite{Wray02,Wray08}, wherein a formulaic sequence (FS) is defined as ``a sequence, continuous or discontinuous, of words or other elements, which is, or appears to be, prefabricated: that is, stored and retrieved whole from memory at the time of use, rather than being subject to generation or analysis by the language grammar.'' That is, a FS shows signs of being part of a mental lexicon. Though by this definition individuals or small groups may have their own FS, here we are only interested in FSs that are shared by a recognizable language community.

In computational linguistics, the most common term used to describe multiword lexical units is \emph{multiword expression} (``MWE'': \newcite{Sag02}, \newcite{Baldwin10}), but here we wish to make a principled distinction between at least somewhat non-compositional, strongly lexicalized MWEs and FS, a near superset which includes many MWEs but also compositional linguistic formulas. This distinction is not a new one; it exists, for example, in the original paper of \newcite{Sag02} in the distinction between lexicalized and institutionalized phrases, and also to some extent in the MWE annotation of \newcite{Schneider14a}, who distinguish between weak (collocational)\footnote{Here we avoid the term \emph{collocation} entirely due to confusion with respect to its interpretation. Though some define it similarly to our definition of FS, it can be applied to any words that show a statistical tendency to appear in the vicinity of one another for any reason: for instance, the pair of words \ex{doctor/nurse} might be considered a collocation \cite{Ramisch14}.}  and strong (non-compositional) MWEs. It is our contention, however, that separate, precise terminology is useful for research targeted at either class: we need not strain the concept of MWE to include items which do not require special semantics, nor are we inclined to disregard the larger formulaticity of language simply because it is not the dominant focus of MWE research. Many MWE researchers might defensibly balk at including in their MWE lexicons and corpus annotations (English) FS such as \ex{there is something going on}, \ex{it is more important than ever to \dotts}, \ex{\dotts do not know what it is like to \dotts}, \ex{there is no shortage of\dotts}, \ex{the rise and fall of\dotts}, \ex{now is not the time to\dotts}, \etc as well as tens of thousands of other such phrases which, along with less compositional MWEs like \ex{be worth \dotts's weight in gold}, fall under the FS umbrella. Another reason to introduce a different terminology is that there are classes of what is typically considered MWE that do not fit well into an FS framework, for instance novel compound nouns whose semantics are accessible by analogy (\eg \ex{glass limb} or \ex{government ambiguity}). Also, we exclude from the definition of both FS and MWE those named entities which refer to people or places which are little-known and/or whose surface form appears derived (\eg \ex{Mrs.\ Barbara W.\ Smith} or \ex{Smith Garden Supplies Ltd}). \figref{fig:terminology} shows the conception of the relationship between FS, MWE, and (multiword) named entities that we assume for this paper.

@@

Regardless of the terminology used to describe them, the starting point for multiword lexicon creation has typically been lexical association measures \cite{Church90,Dunning93,Schone01,Evert04,Pecina10,DeAraujo11,Kulkarni11,Ramisch14}. When these methods are used to build a lexicon, particular binary syntactic patterns are typically chosen. Only some of these measures generalize tractably beyond two words, for example PMI \cite{Church90}, i.e., the log ratio of the joint probability to the product of the marginal probabilities of the individual words. Other measures specifically designed to address sequences of larger than two words include: the $c$-value \cite{Frantzi00}, a metric designed for term extraction which weights term frequency by the log length of the $n$-gram while penalizing $n$-grams that appear in frequent larger ones; and mutual expectation \cite{Dias99}, which produces a normalized statistic that reflects how much a candidate phrase resists the omission of any particular word. Similarly, the lexical predictability ratio (LPR) of \newcite{Brooke15b} is an association measure intended for any possible syntactic pattern which is calculated by discounting syntactic predictability from the overall conditional probability for each word given the other words in the phrase. Though most association measures involve only usage statistics of the phrase and its subparts, the DRUID measure is an exception which uses distributional semantics around the phrase to identify how easily an $n$-gram could be replaced by a single word \cite{Riedl15}.

@@

The motivation for building lexicons of FS naturally overlaps with those for MWE: models of distributional semantics, in particular, can benefit from sensitivity to multiword units \cite{Cohen:Widdows:2009}, as can parsing \cite{Constant16} and topic models \cite{Lau+:2012b}. One major motivation for looking beyond MWEs is the ability to carry out broader linguistic analyses. Within corpus linguistics, multiword sequences have been studied in the form of \textit{lexical bundles} \cite{Biber04}, which are simply $n$-grams that occur above a certain frequency threshold. Like FS, Lexical bundles generally involve larger phrasal chunks that would be missed by traditional MWE extraction, and so research in this area has tended to focus on how particular formulaic phrases (\eg \textit{if you look at}) are indicative of particular genres (\eg university lectures). Lexical bundles have been applied, in particular, to learner language: for example,  \newcite{Chen10} show that non-native student writers use a severely restricted range of lexical bundle types, and tend to overuse those types, while \newcite{Granger14} investigate the role of proficiency, demonstrating that intermediate learners underuse lower-frequency bigrams and overuse high-frequency bigrams relative to advanced learners. \newcite{Sakaguchi16} demonstrate that improving fluency (closely linked to the use of linguistic formulas) is more important than improving strict grammaticality with respect to native speaker judgments of non-native productions; \newcite{Brooke15b} explicitly argue for FS lexicons as a way to identify, track, and improve learner proficiency.

@@

Our approach to FS identification involves optimization of the total explanatory power of a lattice, where each node corresponds to an $n$-gram type. The explanatory power of the whole lattice is defined simply as a product of the \termdef{explainedness} of the individual nodes. Each node can be considered either ``on'' (is an FS) or ``off'' (is not an FS). The basis of \termdef{explainedness} calculation is the syntax-sensitive LPR association measure of \newcite{Brooke15b}, but it is calculated differently depending on the on/off status of the node as well as the status of the nodes in the vicinity: nodes are linked based on $n$-gram subsumption and corpus overlap relationships (see \figref{fig:example}), with ``on'' nodes typically explaining other nodes.  Given these relationships, we iterate over the nodes and greedily optimize the on/off choice relative to explainedness in the local neighborhood of each node, until convergence.

@@

The first step in the process is to derive a set of $n$-grams and related statistics from a large, unlabeled corpus of text. Since our primary association measure is an adaption of LPR, our approach in this section mostly follows \newcite{Brooke15b} up until the last stage. An initial requirement of any such method is an $n$-gram frequency threshold, which we set to 1 instance per 10 million words, following \newcite{Brooke15b}.\footnote{Based on manual analysis using the MWE corpus of \newcite{Schneider14a}, this achieves very good (over 90\%) type-level MWE coverage using the frequency filtered $n$-gram statistics from the ICWSM blog corpus (see \secref{sec:evaluation}) after filtering out proper names.}

We include gapped or non-contiguous $n$-grams in our analysis, in acknowledgment of the fact that many languages have MWEs where the components can be ``separated'', including verb particle constructions in English \cite{Dehe:2002}, and noun--verb idioms in Japanese \cite{Hashimoto:Kawahara:2008}. Having said this, there are generally strong syntactic and length \cite{Wasow:2002} restrictions on what can constitute a gap, which we capture in the form of a language-specific POS-based regular expression (see \secref{sec:evaluation} for details).
This greatly lowers the number of potentially gapped $n$-gram types, increasing precision and efficiency for negligible loss of recall. We also exclude punctuation and lemmatize the corpus, and enforce an $n$-gram count threshold. As long as the count threshold  is substantially above 1, efficient extraction of all $n$-grams can be done iteratively: in iteration $i$, $i$-grams are filtered by the frequency threshold, and then pairs of instances of these $i$-grams with $(i-1)$ words of overlap are found, which derives a set of $(i+1)$-grams which necessarily includes all those over the frequency threshold.

Once a set of relevant $n$-grams is identified and counted, other statistics required to calculate the \termdef{Lexical Predictability Ratio} (``LPR'') for each word in the $n$-gram are collected. LPR is a measure of how predictable a word is in a lexical context, as compared to how predictable it is given only syntactic context (over the same span of words). Formally, the LPR for word $w_i$ in the context of a word sequence $w_1,..., w_i, ..., w_{n}$ with POS tag sequence $t_1, ..., t_{n}$, is given by:
\begin{displaymath}
\LPR(w_i,w_{1,n}) = \max_{1 \leq j < k \leq n }{\frac{p(w_i|w_{j,k})}{p(w_i|t_{j,k})}}
\end{displaymath}
where $w_{j,k}$ denotes the word sequence $w_j,..., w_{i-1}, w_{i+1}, ..., w_{k}$ excluding $w_{i}$ (similarly for $t_{j,k}$). Note that the lower bound of LPR is 1, since the ratio for a word with no context is trivially 1. We use the same equation for gapped $n$-grams, with the caveat that quantities involving sequences which include the location where the gap occurs are derived from special gapped $n$-gram statistics. %Note that the identification of the best ratio across all possible choices of context, not just the largest, is important for longer FS, where the entire POS context alone might uniquely identify the phrase, resulting in the minimum LPR of 1 even for entirely formulaic sequences, an undesirable result.

In the segmentation approach of \newcite{Brooke15b}, LPR for an entire span is calculated as a product of the individual LPRs, but here we will use the minimum LPR across the words in the sequence:
\begin{displaymath}
\minLPR(w_{1,n}) = \min_{1 \leq i \leq n }{\LPR(w_i,w_{1,n})}
\end{displaymath}
Here, minLPR for a particular $n$-gram does not reflect the \emph{overall} degree to which it holds together, but rather focuses on the word which is its weakest link. For example, in the case of \ex{be keep \gap under}, a general statistical metric might assign it a high score due to the strong association between \ex{keep} and \ex{under}, but minLPR is focused on the weaker relationship between \ex{be} and \ex{keep \gap under}.

@@

Let $E_{1}$ be the explainedness of a node when it is on (corresponding to an $n$-gram which has been identified as an FS), and $E_{0}$ be the explainedness of a node when it is off. We calculate $E_{0}$ based on the inverse of minLPR: 
\begin{displaymath}
E_0(t) = \minLPR(t)^{-d_0(t)}
\end{displaymath}
and $E_{1}$ based on the inverse of a cost parameter $C$:
\begin{displaymath}
E_1(t) = C^{-d_1(t)}
\end{displaymath}
where $d_0$ and $d_1$ are non-negative functions which capture the lattice context (when there is no context, both default to 1), as detailed in the next section. When the minLPR metric is 1 (corresponding to the case of the syntactic content predicting one of the words of the $n$-gram as well or better than the lexical context), $E_{0}=1$. $E_1$ is equivalent to the initial threshold for building a vocabulary using the minLPR association measure for nodes not influenced by one of the other factors discussed below: all else being equal, when $\minLPR(t) > C$, a node will be selected as an FS. There is no upper bound on $C$, but empirically, we have found a value in the range $[3,6]$ gives reasonable results for the languages presented in this paper.% we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) results in too much random noise.

@@

\subsubsection{Covering}
The most important node interaction is \termdef{covering}, which corresponds to discounting or entirely excluding a node due to a node higher in the lattice. Our model includes two types of covering: hard and soft.

\termdef{Hard covering} is based on the idea that, due to very similar counts, we can reasonably conclude that the presence of an $n$-gram in our statistics is a direct result of the other. In \figref{fig:example}, \eg if we have 143 counts of \ex{keep \gap under wraps} and 152 counts of \ex{under wraps}, the presence of \ex{keep \gap under wraps} almost completely explains \ex{under wraps}, and we should consider these two $n$-grams as one. We do this by permanently disabling any hard covered node, and setting the minLPR of the covering node to the maximum minLPR among all the nodes it covers (including itself); this means that longer $n$-grams with function words (which often have lower minLPR) can benefit from the strong statistical relationships between open-class lexical features in $n$-grams that they cover. This is done as a preprocessing step, and greatly improves the tractability of the iterative optimization of the lattice. Of course, a threshold for hard covering must be chosen: empirically, we have found that a ratio of $2/3$ (corresponding to a significant majority of the counts of a lower node corresponding to the higher node) works well.  We also use the concept of hard covering to address the issue of pronouns, based on the observation that pronouns often have high LPR values \cite{Brooke15b}. In the lattice, $n$-grams with pronouns are considered covered (inactive) unless they cover at least one other node which does not have a pronoun, which allows us to limit FS with pronouns without excluding them entirely: they are included only in cases where they are definitively formulaic.

@@

A simple but effective solution which avoids introducing extra hyperparameters is to make use of the minLPR values of the relevant nodes. In the most common two-node situation, we increase $E_{0}$ of the higher node based on the ratio of the minLPR of two nodes, though only if the minLPR of the lower node is higher. Generalized to the (rare) case of multiple clearing nodes, we define $\clear(t)$ as:
%in this paper, we consider two options: a hard clearing where any turned-on node will clear (set $C_{0}$ to 0 for) any node higher in the lattice which has a minLPR that is lower than it; and a soft 
\begin{displaymath}
\clear(t) = \prod_{i=1}^{m}{\min\Big(1,\frac{\minLPR(t)}{\minLPR(u_i)}\Big)}
\end{displaymath}
where $u_i$ is the $i$th clearing node of $t$. We refer to this mechanism as ``clearing'' because it tends to clear away a variety of trivial uses of common FS which may have higher LPR due to the lexical and syntactic specificity of the FS. For instance, in \figref{fig:example} if the node \ex{keep \gap under wraps}  is turned on and has a minLPR of 8, then, if the minLPR of a node such as \ex{keep \gap under wraps for} is 4, $\clear(t)$ will be 0.5.

@@

The third mechanism of node interaction involves $n$-grams which overlap in the corpus. In general, independent FS do not predictably overlap. For example, given that \ex{be keep \gap under} and \ex{keep \gap under wraps} often appear together (overlapping on the tokens \ex{keep \gap under}), we do not want both being selected as an FS, even in the case that both have high minLPR. To address this problem, we use a mechanism somewhat different than above: rather than increasing the explainedness of turned-off nodes, we decrease the explainedness of the overlapping turned-on nodes---a penalty rather than an incentive which expresses the model's confusion at having overlapping FS. Let $\mathit{oc}(x,y)$ refer to number of times the $n$-grams corresponding to nodes $x$ and $y$ overlapped in the corpus, and $o_1,\dotts,o_m$ refer to turned-on nodes which overlap with our target node $t$. We define $d_1(t)$, the exponential term for $E_1(t)$, as:
\begin{displaymath}
	d_{1}(t) = \frac{c(t)}{c(t) - \sum_{i=1}^{m}{\mathit{oc}(o_i)}}
\end{displaymath}

@@

\newcite{Brooke15b} introduced a method for evaluating FS extraction without a reference lexicon or direct annotation of the output of a model. Instead, $n$-grams are sampled after applying the frequency threshold and annotated as being either an FS or not, allowing for calculation of a true F-score for any model. We use the annotation of 2000 $n$-grams in the ICWSM corpus from that earlier work, and applied the same annotation methodology to the other corpora discussed above: after training and based on written guidelines derived from the definitions of \newcite{Wray08}, three native-speaker, educated annotators judged 500 contiguous $n$-grams and another 500 gapped $n$-grams for each of the new corpora.

@@

 \begin{center}
   \begin{tabular}{lc@{\,\,\,}cc@{\,\,\,}c@{\,\,\,}c}

       \toprule
       & \multicolumn{2}{c}{Contiguous} & \multicolumn{2}{c}{Gapped} & \multirow{2}{*}{$\kappa$}\\
       \cmidrule(lr){2-3}\cmidrule(lr){4-5}
			& FS & non-FS & FS & non-FS &  \\
			 \midrule
			ICWSM    & 169  & 702 & 29 & 916 & 0.84 \\
			BNC      & \z49 & 403 & \z8& 475 & 0.84 \\
			Croatian & \z64 & 382 & 11 & 456 & 0.87 \\
			Japanese & 124  & 286 & 36 & 341 & 0.81\\
       \bottomrule
 \end{tabular}
  \caption{ Statistics for test sets }
	 \label{tab:stats}

@@

@@

 \end{tabular}
  \caption{ Results of FS identification in various test sets; PMIrank = lexicon created by ranking pointwise mutual information, minLPRrank = lexicon created by ranking by minLPR, LPRseg = lexicon created by method of Brooke at \al (2015), -cl = no clearing, -ovr = no penalization of overlaps, P = Precision, R = Recall, F = F-score. Bold is best in column.}
	 \label{tab:main}

@@

       \toprule
			& P & R & F\\
			 \midrule
			PMIrank & 0.20 & 0.29 & 0.23 \\
			minLPRrank & 0.34 & 0.45 & 0.39 \\
			LPR-seg & 0.42 & 0.45 & 0.43 \\
			LocalMaxs & \bf{0.56} & 0.39 & 0.46 \\
			DP-seg & 0.35 & \bf{0.71} & 0.47 \\
  \midrule
			Lattice & 0.47 & 0.63 & \bf{0.54} \\
       \bottomrule
 \end{tabular}
  \caption{ Results of FS identification in contiguous BNC test set; LocalMaxs = method of Silva and Lopes (1999); DP-seg = method of Newman et \al (2012)}
	\label{tab:BNC}
